### 2017-11-14 Docs/Thesis/docs/chapter5.tex
>>>>>update in some scripts...BUGS.... actually I'm using this version on the thesis....<<<<<<

We use SIMITAR v0.4.2 (Eulemur rubriventer)\foornote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List_of_lemur_species})}, as tagged at the GitHub repository.  SIMITAR already have two functional traffic generator engines: Iperf and libtins C++ API.

@@

\begin{table}[ht!]
	\centering
	\caption{My caption}
	\label{my-label}
	\begin{tabular}{lllll}
		\hline
		& skype-pcap & simitar iperf one-hop & simitar iperf tree & simitar libtins \\ \hline
		Hurst Exponent                  &            &                       &                    &                 \\
		Data bit rate (kbps)            &            &                       &                    &                 \\
		Average packet rate (packets/s) &            &                       &                    &                 \\
		Average packet size (bytes)     &            &                       &                    &                 \\
		Number of packets               &            &                       &                    &                 \\ \hline
	\end{tabular}
\end{table}

% Flows per second
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfFlowsPs.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowsPs.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowsPs.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flow per seconds}
	\label{fig:flows-ps}
\end{figure}
% Bandwidth
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfBandwidth.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeBandwidth.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsBandwidth.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Traces bandwidth.}
	\label{fig:flows-bandwidth}
\end{figure}
% Flow CDF
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfFlowCdf.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeFlowCdf.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsFlowCdf.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flows cumulative distributions.}
	\label{fig:flows-cdf}
\end{figure}
% Wabelet
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperfWaveletMREA.pdf}
		\label{fig:iperfWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/iperftreeWaveletMREA.pdf}
		\label{fig:iperftreeWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
		\label{fig:tinsWaveletMREA}
	}
	\hspace{0mm}
		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
			\includegraphics[width=77mm]{figures/ch5/tinsWaveletMREA.pdf}
			\label{fig:tinsLgwWaveletMREA}
		}
		\hspace{0mm}
	\caption{Wavelet multiresolution energy analysis.}
	\label{fig:wavelet}
\end{figure}

>>>>

We use SIMITAR v0.4.2 (Eulemur rubriventer)\footnote{ We label the tags of SIMITAR control version on GitHub as lemurs species names (\href{https://en.wikipedia.org/wiki/List_of_lemur_species}{https://en.wikipedia.org/wiki/List\_of\_lemur\_species})}, as tagged at the GitHub repository.  SIMITAR already have two functional traffic generator engines: Iperf and libtins C++ API.

@@

\begin{table}[ht!]
	\centering
	\caption{Sumary of results comparing the original traces (italic) and te traffic generated by SIMITAR, with the description of the scenario.}
	\label{my-label}
	\scalebox{0.87}{
\begin{tabular}{lcccccc}
	\hline
	\multicolumn{1}{c}{\multirow{3}{*}{}} & \multirow{3}{*}{\textit{skype-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ tree, \\ iperf\end{tabular}}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}skype, \\ one-hop, \\ libtins\end{tabular}}} & \multirow{3}{*}{\textit{lgw10s-pcap}} & \multicolumn{1}{c}{\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}lgw10s, \\ one-hop, \\ libtins\end{tabular}}} \\
	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\
	\multicolumn{1}{c}{}                  &                             & \multicolumn{1}{c}{}                                                                                     & \multicolumn{1}{c}{}                                                                                  & \multicolumn{1}{c}{}                                                                                       &                              & \multicolumn{1}{c}{}                                                                                        \\ \hline
	Hurst Exponent                        & 0.601                       & 0.618                                                                                                    & 0.598                                                                                                 & 0.691                                                                                                      & 0.723                        & 0.738                                                                                                       \\
	Data bit rate (kbps)                  & 7                           & 19                                                                                                       & 19                                                                                                    & 12                                                                                                         & 7252                         & 6790                                                                                                        \\
	Average packet rate (packets/s)       & 3                           & 4                                                                                                        & 5                                                                                                     & 6                                                                                                          & 2483                         & 2440                                                                                                        \\
	Average packet size (bytes)           & 260,89                      & 549,05                                                                                                   & 481,14                                                                                                & 224,68                                                                                                     & 365,00                       & 347,85                                                                                                      \\
	Number of packets                     & 1071                        & 1428                                                                                                     & 1604                                                                                                  & 2127                                                                                                       & 24 k                         & 24 k                                                                                                        \\
	Number of flows                       & 167                         & 350                                                                                                      & 325                                                                                                   & 162                                                                                                        & 3350                         & 3264                                                                                                        \\ \hline
\end{tabular}
	}
\end{table}

% Flows per second
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowsPs.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowsPs.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowsPs.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowsPs.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flow per seconds}
	\label{fig:flows-ps}
\end{figure}
% Bandwidth
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-Bandwidth.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-Bandwidth.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-Bandwidth.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-Bandwidth.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Traces bandwidth.}
	\label{fig:flows-bandwidth}
\end{figure}
% Flow CDF
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-FlowCdf.pdf}
		\label{fig:iperfCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-FlowCdf.pdf}
		\label{fig:iperftreeCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-FlowCdf.pdf}
		\label{fig:tinsCdf}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/lgw-tins-FlowCdf.pdf}
		\label{fig:tinsLgwCdf}
	}
	\hspace{0mm}
	\caption{Flows cumulative distributions.}
	\label{fig:flows-cdf}
\end{figure}
% Wabelet
\begin{figure}[h!]
	\centering
	\subfloat[\textit{Iperf, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-iperf-WaveletMREA.pdf}
		\label{fig:iperfWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{Iperf, tree, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tree-iperf-WaveletMREA.pdf}
		\label{fig:iperftreeWaveletMREA}
	}
	\hspace{0mm}
	\subfloat[\textit{libtins, single-hop, skype-pcap}]{
		\includegraphics[width=77mm]{figures/ch5/skype-tins-WaveletMREA.pdf}
		\label{fig:tinsWaveletMREA}
	}
	\hspace{0mm}
		\subfloat[\textit{libtins, single-hop, langw10s-pcap}]{
			\includegraphics[width=77mm]{figures/ch5/lgw-tins-WaveletMREA.pdf}
			\label{fig:tinsLgwWaveletMREA}
		}
		\hspace{0mm}
	\caption{Wavelet multiresolution energy analysis.}
	\label{fig:wavelet}
\end{figure}
